# -------------------------------------------------------------------
# Purpose:
#   Homogeneous Markov Chain (MC) imputation for BE + simulation-based evaluation.
#
# Workflow:
#   1) Load and prepare data (generate lag variables for MC conditioning)
#   2) Load helper functions (masking, MC imputation, evaluation)
#   3) Run simulations for block_length = 1..6 (n_sim = 30, fixed seed) for different Markov orders (MC2–MC4; optional)
#   4) Save results (RData + CSV summaries)
#
# Key settings (used below):
#   - sampling_rate = 0.1
#   - block_length  = 1..6
#   - n_sim         = 30
#   - seed          = 123 (seed + s per simulation run)
#   - MC scenarios correspond to Markov order h:
#       MC1: h = 1 (default)
#       MC2: h = 2 (optional)
#       MC3: h = 3 (optional)
#       MC4: h = 4 (optional)
#
# Outputs:
#   outputs/MC results/ (RData checkpoints + final RData + CSV summaries)
# -------------------------------------------------------------------


# Set the working directory to the current file's location.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


if (interactive() && requireNamespace("rstudioapi", quietly = TRUE)) {
  current_path <- dirname(rstudioapi::getSourceEditorContext()$path)
  setwd(current_path)
  message("Working directory successfully set to: ", current_path)
}
```

# Load Packages:
# - Data wrangling: dplyr, tidyr, purrr, rlang
# - I/O: haven
# - Imputation helpers: zoo
# - Evaluation metrics: psych, Metrics
# - Plotting: ggplot2
```{r}
library(haven)
library(tidyr)
library(purrr)
library(Metrics)
library(zoo)
library(rlang)
library(psych)
library(dplyr)
library(ggplot2)
```

# Load Dataset
# We use the prepared panel dataset for imputation evaluation.
# Note: simulation repeats n_sim times; runtime can be substantial on the full sample of read data
```{r}
filled.data <- read_dta("../../Dataset/imputation_data.dta")
```

# Generate lagged versions of BS and BE each firm (idnum).
# These lags are used to form lag-pattern conditions for the Markov Chain imputation.
```{r}
filled.data <- filled.data%>%
  arrange(idnum, shift_date) %>%         
  group_by(idnum) %>%              
  mutate(
    vg_statebus_lag1 = lag(vg_statebus, 1),    
    vg_statebus_lag2 = lag(vg_statebus, 2),    
    vg_statebus_lag3 = lag(vg_statebus, 3),
    vg_statebus_lag4 = lag(vg_statebus, 4),    
    vg_comexp_lag1 = lag(vg_comexp, 1),    
    vg_comexp_lag2 = lag(vg_comexp, 2),    
    vg_comexp_lag3 = lag(vg_comexp, 3),    
    vg_comexp_lag4 = lag(vg_comexp, 4)
  ) %>%
  ungroup()
```

# Load helpers
```{r}
source("../helpers/MC_helpers.R")
```

# Simulation
# -------------------------------------------------------------------
# Simulation runs for different missing block lengths.
# We keep sampling_rate = 0.1 and n_sim = 30 fixed, and vary block_length = 1..6.
# Results are stored as a list with:
#   - $all_runs: metrics per simulation run
#   - $summary: average metrics across runs
# -------------------------------------------------------------------

## MC1
```{r}
# Defined Constants
N_SIM <- 30
SEED  <- 123
SAMPLING_RATE <- 0.1
BLOCK_LENGTHS <- 1:6

for (k in BLOCK_LENGTHS) {
  message(paste("\n>>> Starting Scenario: Block Length =", k, "<<<"))
  
  # 1. Run the simulation
  current_result <- simulate_imputation_evaluation(
    df = filled.data,             
    var = "vg_comexp",              
    id = "idnum",
    time = "shift_date",
    mask_fun = simulate_mask_row,
    # Dynamic block_length for masking
    mask_args = list(block_length = k, sampling_rate = SAMPLING_RATE),
    impute_fun = impute_masked_mc,    
    impute_args = list(
      mask_flag = "is_masked",
      h = 1,
      lag_list = c('vg_comexp_lag1',
                   'vg_comexp_lag2',
                   'vg_comexp_lag3',
                   'vg_comexp_lag4'),
      strategy = 'mode'
    ),
    n_sim = N_SIM,
    seed = SEED
  )
  
  # 2. Assign the result to a specific variable name
  assign(paste0("sim_mc1_result_", k), current_result)
  
  # Intermediate save
  if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)
  save(list = ls(pattern = "^sim_mc1_result_"), file = 'outputs/MC results/MC_BE_res1_temp.RData')
}
```
## MC2(optional)
```{r}

for (k in BLOCK_LENGTHS) {
  message(paste("\n>>> Starting Scenario: Block Length =", k, "<<<"))
  
  # 1. Run the simulation
  current_result <- simulate_imputation_evaluation(
    df = filled.data,             
    var = "vg_comexp",              
    id = "idnum",
    time = "shift_date",
    mask_fun = simulate_mask_row,
    # Dynamic block_length for masking
    mask_args = list(block_length = k, sampling_rate = SAMPLING_RATE),
    impute_fun = impute_masked_mc,    
    impute_args = list(
      mask_flag = "is_masked",
      h = 2,
      lag_list = c('vg_comexp_lag1',
                   'vg_comexp_lag2',
                   'vg_comexp_lag3',
                   'vg_comexp_lag4'),
      strategy = 'mode'
    ),
    n_sim = N_SIM,
    seed = SEED
  )
  
  # 2. Assign the result to a specific variable name
  assign(paste0("sim_mc2_result_", k), current_result)
  
  # Intermediate save
  if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)
  save(list = ls(pattern = "^sim_mc2_result_"), file = 'outputs/MC results/MC_BE_res2_temp.RData')
}
```

# MC3(optional)
```{r}
for (k in BLOCK_LENGTHS) {
  message(paste("\n>>> Starting Scenario: Block Length =", k, "<<<"))
  
  # 1. Run the simulation
  current_result <- simulate_imputation_evaluation(
    df = filled.data,             
    var = "vg_comexp",              
    id = "idnum",
    time = "shift_date",
    mask_fun = simulate_mask_row,
    # Dynamic block_length for masking
    mask_args = list(block_length = k, sampling_rate = SAMPLING_RATE),
    impute_fun = impute_masked_mc,    
    impute_args = list(
      mask_flag = "is_masked",
      h = 3,
      lag_list = c('vg_comexp_lag1',
                   'vg_comexp_lag2',
                   'vg_comexp_lag3',
                   'vg_comexp_lag4'),
      strategy = 'mode'
    ),
    n_sim = N_SIM,
    seed = SEED
  )
  
  # 2. Assign the result to a specific variable name
  assign(paste0("sim_mc3_result_", k), current_result)
  
  # Intermediate save
  if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)
  save(list = ls(pattern = "^sim_mc3_result_"), file = 'outputs/MC results/MC_BE_res3_temp.RData')
}
```


# MC4(optional)
```{r}

for (k in BLOCK_LENGTHS) {
  message(paste("\n>>> Starting Scenario: Block Length =", k, "<<<"))
  
  # 1. Run the simulation
  current_result <- simulate_imputation_evaluation(
    df = filled.data,             
    var = "vg_comexp",              
    id = "idnum",
    time = "shift_date",
    mask_fun = simulate_mask_row,
    # Dynamic block_length for masking
    mask_args = list(block_length = k, sampling_rate = SAMPLING_RATE),
    impute_fun = impute_masked_mc,    
    impute_args = list(
      mask_flag = "is_masked",
      h = 4,
      lag_list = c('vg_comexp_lag1',
                   'vg_comexp_lag2',
                   'vg_comexp_lag3',
                   'vg_comexp_lag4'),
      strategy = 'mode'
    ),
    n_sim = N_SIM,
    seed = SEED
  )
  
  # 2. Assign the result to a specific variable name
  assign(paste0("sim_mc4_result_", k), current_result)
  
  # Intermediate save
  if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)
  save(list = ls(pattern = "^sim_mc4_result_"), file = 'outputs/MC results/MC_BE_res4_temp.RData')
}
```

# Save Results
```{r}

if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)

result_objects <- ls(pattern = "^sim_mc")

manual_objects <- c(
  "filled.data",                    
  "impute_masked_mc",                
  "simulate_mask_row",               
  "simulate_imputation_evaluation",  
  "N_SIM", "SEED", "SAMPLING_RATE", "BLOCK_LENGTHS" 
)
objects_to_save <- c(result_objects, manual_objects)
save(list = objects_to_save, file = 'outputs/MC results/MC_BE_res.RData')
```


# Output files:
# - mc1_all_runs_result_k.csv: per-simulation metrics (one row per run)
# - mc1_summary_k.csv: averaged metrics across n_sim runs
# where k corresponds to missing block length (block_length = 1..6).
#
# For MC2/MC3/MC4 , their outputs follow the same naming convention:
# - mc2_all_runs_result_k.csv / mc2_summary_k.csv, etc.
```{r}
if(!dir.exists("outputs/MC results")) dir.create("outputs/MC results", recursive = TRUE)


# Save MC1 Results

for (k in 1:6) {
  var_name <- paste0("sim_mc1_result_", k)
  res <- get(var_name)
  file_all <- paste0("outputs/MC results/mc1_all_runs_result_", k, ".csv")
  file_sum <- paste0("outputs/MC results/mc1_summary_", k, ".csv")
  write.csv(res$all_runs, file_all, row.names = TRUE)
  write.csv(res$summary,  file_sum, row.names = TRUE)
  message("Saved MC1: ", file_sum)
}


# Save MC2 Results (Loop)
# for (k in 1:6) {
#   var_name <- paste0("sim_mc2_result_", k)
#   res <- get(var_name)
#   file_all <- paste0("outputs/MC results/mc2_all_runs_result_", k, ".csv")
#   file_sum <- paste0("outputs/MC results/mc2_summary_", k, ".csv")
#   write.csv(res$all_runs, file_all, row.names = TRUE)
#   write.csv(res$summary,  file_sum, row.names = TRUE)
#   message("Saved MC2: ", file_sum)
# }


# Save MC3 Results

# for (k in 1:6) {
#   var_name <- paste0("sim_mc3_result_", k)
#   res <- get(var_name)
#   file_all <- paste0("outputs/MC results/mc3_all_runs_result_", k, ".csv")
#   file_sum <- paste0("outputs/MC results/mc3_summary_", k, ".csv")
#   write.csv(res$all_runs, file_all, row.names = TRUE)
#   write.csv(res$summary,  file_sum, row.names = TRUE)
#   message("Saved MC3: ", file_sum)
# }


# Save MC4 Results (Loop) - Commented Out

# for (k in 1:6) {
#   var_name <- paste0("sim_mc4_result_", k)
#   res <- get(var_name)
#   file_all <- paste0("outputs/MC results/mc4_all_runs_result_", k, ".csv")
#   file_sum <- paste0("outputs/MC results/mc4_summary_", k, ".csv")
#   write.csv(res$all_runs, file_all, row.names = TRUE)
#   write.csv(res$summary,  file_sum, row.names = TRUE)
#   message("Saved MC4: ", file_sum)
# }
```