# -------------------------------------------------------------------
# Purpose:
#   Random Forest (RF) imputation for BE + simulation-based evaluation.
#   Covariates are pre-imputed using LOCF to obtain a complete feature set for RF.
#
# Workflow:
#   1) Load and prepare data (generate lags, set data types)
#   2) Pre-impute covariates via LOCF (forward + backward fill)
#   3) Load helper functions (masking, rolling RF imputation, evaluation)
#   4) Tune RF hyperparameters via OOB error (optional, used to select mtry/ntree/nodesize)
#   5) Run simulations for block_length = 1..6 (n_sim = 30, fixed seed)
#   6) Save results (RData + CSV summaries) and generate balance plot
#
# Key settings (used below):
#   - sampling_rate = 0.1
#   - block_length  = 1..6
#   - n_sim         = 30
#   - seed          = 123 (seed + s per simulation run)
#   - RF hyperparams used in simulation: mtry = 3, num.trees = 350, min.node.size = 1
#
# Outputs:
#   outputs/RF results/ (CSV files + RData + balance plot PDF)
# -------------------------------------------------------------------


# Set the working directory to the current file's location.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


if (interactive() && requireNamespace("rstudioapi", quietly = TRUE)) {
  current_path <- dirname(rstudioapi::getSourceEditorContext()$path)
  setwd(current_path)
  message("Working directory successfully set to: ", current_path)
}
```
# Load Packages:
# - Data wrangling: dplyr, tidyr, purrr, rlang
# - I/O: haven
# - Imputation helpers: zoo, missForest
# - Random forest: randomForest, ranger, caret
# - Evaluation metrics: psych, Metrics
```{r}
library(haven)
library(tidyr)
library(purrr)
library(Metrics)
library(rlang)
library(psych)
library(dplyr)
library(missForest)
library(caret)
library(randomForest)
library(ranger)
library(zoo)
library(ggplot2)
```

# Load Dataset
# We use the prepared panel dataset for imputation evaluation.
# Note: simulation repeats n_sim times; runtime can be substantial on the full sample of read data
```{r}
filled.data <- read_dta("../../Dataset/imputation_data.dta")
```


# Generate lagged versions of BS and BE (1–4 lags) within each firm (idnum).
# These lags serve as predictors for RF, especially for rolling imputation within masked blocks.
```{r}
filled.data <- filled.data%>%
  arrange(idnum, shift_date) %>%         
  group_by(idnum) %>%              
  mutate(
    vg_statebus_lag1 = lag(vg_statebus, 1),    
    vg_statebus_lag2 = lag(vg_statebus, 2),    
    vg_statebus_lag3 = lag(vg_statebus, 3),
    vg_statebus_lag4 = lag(vg_statebus, 4),    
    vg_comexp_lag1 = lag(vg_comexp, 1),    
    vg_comexp_lag2 = lag(vg_comexp, 2),    
    vg_comexp_lag3 = lag(vg_comexp, 3),    
    vg_comexp_lag4 = lag(vg_comexp, 4)
  ) %>%
  ungroup()
```

# Convert covariates to the appropriate data types for RF:
# - Discrete/ordinal variables -> factor
# - Continuous variables -> numeric
```{r}
discrete.covariates <- c('idnum','vg_westeast','sector_total','online','is_dec','is_aug','vg_statebus','vg_comexp')
continuous.covariates <- c('vg_statebus_lag1'
                           ,'vg_statebus_lag2'
                           ,'vg_statebus_lag3'
                           ,'vg_statebus_lag4'
                           ,'vg_comexp_lag1'
                           ,'vg_comexp_lag2'
                           ,'vg_comexp_lag3'
                           ,'vg_comexp_lag4'
                           ,'calendar_time')
filled.data <- filled.data%>%
  mutate(across(all_of(discrete.covariates), as.factor))%>%
  mutate(across(all_of(continuous.covariates), as.numeric))
filled.data <- as.data.frame(filled.data)
```

# Pre-imputation of covariates:
# RF requires a complete feature set. We therefore fill missing values in covariates
# using LOCF forward-fill + backward-fill (NOCB) within each id.
# The target variable (vg_statebus) is NOT imputed here; it will be masked and imputed later.


```{r}
# covariates list
all.covariates1 <- c('idnum','vg_westeast','sector_total','online'
                ,'vg_statebus_lag1'
                ,'vg_statebus_lag2'
                ,'vg_statebus_lag3'
                ,'vg_statebus_lag4'
                ,'vg_comexp_lag1'
                ,'vg_comexp_lag2'
                ,'vg_comexp_lag3'
                ,'vg_comexp_lag4'
                ,'calendar_time'
                ,'is_dec'
                ,'is_aug')

# We do not impute idnum; all other covariates are filled.
vars_to_impute <- setdiff(all.covariates1, "idnum")

new.filled.data <- filled.data %>%
  arrange(idnum, shift_date) %>%
  group_by(idnum) %>%
  mutate(across(
    all_of(vars_to_impute),
    # Two-pass fill: forward LOCF, then backward LOCF to fill leading NAs.
    ~ na.locf(na.locf(., na.rm = FALSE), fromLast = TRUE, na.rm = FALSE)
  )) %>%
  ungroup()

```

# Load helpers
```{r}
source("../helpers/RF_helpers.R")
```


# Hyperparameter tuning (optional):
# Use OOB error from ranger to select (mtry, num.trees, min.node.size) on non-missing target rows.
# The selected parameters are then used consistently in the simulation section below.
# Note: we use the tuning results based on real data(not test data) to keep consistency, which does not influence debugging
```{r}

var <- 'vg_comexp'
df <- new.filled.data

# Formula
formula_rf <- as.formula(paste(var, "~", paste(all.covariates1, collapse = "+")))

# Only take rows with no NA targte variable
df_nonmiss <- df[!is.na(df[[var]]), ]

p <- length(all.covariates1)

### -------------------------------------------
### 2. params list
### -------------------------------------------
mtry_candidates  <- c(floor(sqrt(p)), floor(p/3),floor(p/2))
ntree_candidates <- c(200, 350, 500)
nodesize_candidates <- c(1, 3)

param_grid <- expand.grid(
  mtry = mtry_candidates,
  ntree = ntree_candidates,
  nodesize = nodesize_candidates
)

### -------------------------------------------
### 3. OOB error
### -------------------------------------------
results <- data.frame(
  mtry = integer(),
  ntree = integer(),
  nodesize = integer(),
  OOB_error = numeric()
)

# Loop over parameter grid and record OOB classification error.
for (i in 1:nrow(param_grid)) {

  params <- param_grid[i, ]

  cat("Running model", i, "/", nrow(param_grid),
      ": mtry =", params$mtry,
      ", ntree =", params$ntree,
      ", nodesize =", params$nodesize, "\n")

  rf_model <- ranger(
    formula = formula_rf,
    data = df_nonmiss,
    num.trees = params$ntree,
    mtry = params$mtry,
    min.node.size = params$nodesize,
    oob.error = TRUE,
    importance = "none",
    classification = TRUE
  )

  
  oob_err <- rf_model$prediction.error

  results <- rbind(results,
                   data.frame(
                     mtry = params$mtry,
                     ntree = params$ntree,
                     nodesize = params$nodesize,
                     OOB_error = oob_err
                   ))
}

### -------------------------------------------
### 4. res
### -------------------------------------------
results1 <- results[order(results$OOB_error), ]
print(results1)

cat("\nBest parameters:\n")
print(results1[1, ])

```


# -------------------------------------------------------------------
# Simulation runs for different missing block lengths.
# We keep sampling_rate = 0.1 and n_sim = 30 fixed, and vary block_length = 1..6.
# Each run returns:
#   - $all_runs: metrics per simulation run
#   - $summary: average metrics across runs
#   - $imputed_data_list: full imputed data per simulation (incl. prob)
# -------------------------------------------------------------------

```{r}
# Defined Constants
N_SIM <- 30
SEED  <- 123
SAMPLING_RATE <- 0.1
BLOCK_LENGTHS <- 1:6

for (k in BLOCK_LENGTHS) {
  message(paste("\n>>> Starting Scenario: Block Length =", k, "<<<"))
  
  # 1. Run the simulation
  current_result <- simulate_imputation_evaluation(
    df = new.filled.data,             
    var = "vg_comexp",              
    id = "idnum",
    time = "shift_date",
    mask_fun = simulate_mask_row,
    # Dynamic block_length for masking
    mask_args = list(block_length = k, sampling_rate = SAMPLING_RATE),
    impute_fun = impute_masked_rf_rolling,   
    impute_args = list(
      masked_var = "vg_comexp_masked", 
      mask_flag = "is_masked",
      # Dynamic block_length for imputation logic
      block_length = k, 
      id_var = "idnum",
      lag_list = c('vg_comexp_lag1',   
                   'vg_comexp_lag2',
                   'vg_comexp_lag3',
                   'vg_comexp_lag4'),
      covariates = all.covariates1,
      mtry = 3,
      num.trees = 500,                 
      min.node.size = 1
    ),
    n_sim = N_SIM,
    seed = SEED
  )
  
  # 2. Assign the result to a specific variable name
  assign(paste0("sim_result_w_online_", k), current_result)
  
  if(!dir.exists("outputs/RF results")) dir.create("outputs/RF results", recursive = TRUE)
  save(list = ls(pattern = "^sim_result_w_online_"), file = 'outputs/RF results/RF_BE_res_temp.RData')
}

```

# Output files:
# - rf_all_runs_result_w_online_k.csv: metrics for each simulation run (kappa, accuracy, rho.)
# - rf_summary_w_online_k.csv: averaged metrics across runs
# where k corresponds to block_length = 1..6.
```{r}
if(!dir.exists("outputs/RF results")) dir.create("outputs/RF results", recursive = TRUE)

for (k in 1:6) {
  var_name <- paste0("sim_result_w_online_", k)
  res <- get(var_name)
  
  file_all_runs <- paste0("outputs/RF results/rf_all_runs_result_w_online_", k, ".csv")
  file_summary  <- paste0("outputs/RF results/rf_summary_w_online_", k, ".csv")
  
  write.csv(res$all_runs, file_all_runs, row.names = TRUE)
  write.csv(res$summary,  file_summary,  row.names = TRUE)
  
  message("Saved: ", file_summary)
}
```

# Save Results
```{r}
if(!dir.exists("outputs/RF results")) dir.create("outputs/RF results", recursive = TRUE)

result_objects <- ls(pattern = "^sim_result_w_online_")

manual_objects <- c(
  "new.filled.data",                 
  "all.covariates1",                 
  "impute_masked_rf_rolling",       
  "simulate_mask_row",               
  "simulate_imputation_evaluation",  
  "N_SIM", "SEED", "SAMPLING_RATE", "BLOCK_LENGTHS" 
)

objects_to_save <- c(result_objects, manual_objects)

save(list = objects_to_save, file = 'outputs/RF results/RF_BE_res.RData')

```



# Balance check on real data:
# Compute the standard business situation balance over time:
# Balance = (share_more_favourable - share_less_favourable) / n_total
```{r}
var <- 'vg_comexp'
df <- new.filled.data
formula_rf <- as.formula(paste(var, "~", paste(all.covariates1, collapse = "+")))
# only use non-NA rows
rf_model <- ranger(
  formula = formula_rf,
  data = df[!is.na(df[[var]]), ],
    mtry=3,
    num.trees=500,
    min.node.size=1   
)


pred <- predict(rf_model, data = df)$predictions


df <- df %>%
  mutate(
    vg_comexp_imputed = if_else(
      is.na(.data[[var]]),
      pred,                
      .data[[var]]         
    )
  )

df_summary <- df %>%
  group_by(shift_date) %>%
  summarise(
    n_total = n(),
    good_orignal = sum(vg_comexp == 1, na.rm = TRUE),
    bad_orignal  = sum(vg_comexp == 3, na.rm = TRUE),
    Balance_orignal = (good_orignal - bad_orignal) / n_total,
    good_imputed = sum(vg_comexp_imputed == 1, na.rm = TRUE),
    bad_imputed  = sum(vg_comexp_imputed == 3, na.rm = TRUE),
    Balance_imputed = (good_imputed - bad_imputed) / n_total
  )

df_long <- df_summary %>%
  select(shift_date, Balance_orignal, Balance_imputed) %>%
  pivot_longer(cols = c(Balance_orignal, Balance_imputed),
               names_to = "Type",
               values_to = "Balance") %>%
  mutate(
    Type = dplyr::case_when(
          Type == 'Balance_orignal' ~ 'Original Balance',
          Type == 'Balance_imputed' ~ 'Imputed Balance',
          TRUE ~ Type
        ))


rf_be_balance_w_online <- ggplot(df_long, aes(x = shift_date, y = Balance, color = Type)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    #title = "Comparison of BE Balance over Time",
    x = "Time",
    y = "BE Balance",
    color = "Data Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    legend.position = "top"
  )
  
if(!dir.exists("outputs/RF results")) dir.create("outputs/RF results", recursive = TRUE)
ggsave("outputs/RF results/rf_be_balance_w_online.pdf", plot = rf_be_balance_w_online, width = 10, height = 6, units = 'in')

```

