---
title: "Descriptive Analysis: Unit Nonresponse"
date: "2025-12-10"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (interactive() && requireNamespace("rstudioapi", quietly = TRUE)) {
  current_path <- dirname(rstudioapi::getSourceEditorContext()$path)
  setwd(current_path)
  message("Working directory successfully set to: ", current_path)
}
```

# Load Packages
```{r}
library(dplyr)
library(ggplot2)
library(scales)
library(zoo)
library(haven)
library(purrr)
```

# Load Dataset
```{r}
unit_nonresponse_data <- read_dta("../Dataset/unit_nonresponse_data.dta")
```

# Preparation
```{r}
size_labels <- c(
  "1" = "1-99",
  "2" = "100-249",
  "3" = "250-499",
  "4" = "500-999",
  "5" = ">1000",
  "K" = "Small business",
  "S" = "Solo self-employed"
)

sector_names <- tibble(
  sector_total = c(6,7,8,9,10,11,12,13,14,15,16,17,18,19,22,23,24),
  sector_name = c(
    "Food, Drinks & Tobacco",
    "Textile, Clothing, Leather",
    "Wood & Cork Products",
    "Paper & Board Industry",
    "Publishing & Printing",
    "Cokery & Oil Processing",
    "Chemical Industry",
    "Pharmaceutical Industry",
    "Rubber & Plastics",
    "Glass, Ceramics & Stone Processing",
    "Metal Industry",
    "Electronics & Optical Products",
    "Electric Equipment",
    "Machinery Construction",
    "Vehicles & Parts",
    "Furniture, Jewellery, Toys & Others",
    "Other Production"
  )
)

state_names <- tibble(
  fedstaifo = 1:16,
  state_name = c(
    "Berlin West",
    "Schleswig-Holstein",
    "Hamburg",
    "Bremen",
    "Niedersachsen",
    "Nordrhein-Westfalen",
    "Rheinland-Pfalz",
    "Hessen",
    "Baden-Wuerttemberg",
    "Bayern",
    "Saarland",
    "Mecklenburg-Vorpommern",
    "Brandenburg",
    "Sachsen-Anhalt",
    "Sachsen",
    "Thueringen"
  )
)

unit_nonresponse_data_des <- unit_nonresponse_data %>%
  mutate(

    # outcome (binary, keep numeric 0/1 for binomial GAM)
    unit_nonres = unit_nonres,

    # cluster id (numeric, used for clustering only)
    idnum = idnum,

    # East / West
    vg_westeast = factor(
      vg_westeast,
      levels = c(1, 2),
      labels = c("Western", "Eastern")
    ),

    # firm size
    vg_size = factor(
      vg_size,
      levels = names(size_labels),
      labels = unname(size_labels)
    ),

    # online participation
    online = factor(
      online,
      levels = c(0, 1),
      labels = c("Non-online", "Online")
    ),

    # month (Jan–Dec)
    month = factor(
      month,
      levels = 1:12,
      labels = c(
        "Jan", "Feb", "Mar", "Apr", "May", "Jun",
        "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"
      )
    )
  )

unit_nonresponse_data_des <- unit_nonresponse_data_des %>%
  left_join(sector_names, by = "sector_total") %>%
  mutate(
    sector_total = factor(
      sector_total,
      levels = sector_names$sector_total,
      labels = sector_names$sector_name
    )
  ) %>%
  select(-sector_name)

unit_nonresponse_data_des <- unit_nonresponse_data_des %>%
  left_join(state_names, by = "fedstaifo") %>%
  mutate(
    fedstaifo = factor(
      fedstaifo,
      levels = state_names$fedstaifo,
      labels = state_names$state_name
    )
  ) %>%
  select(-state_name)

```

# Unit Nonresonse Rate by Time
```{r}
daily_rate <- unit_nonresponse_data_des %>%
  group_by(shift_date) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = 'drop')

p_des <- ggplot(daily_rate, aes(x = shift_date, y = unit_nonres_rate)) +
  geom_line() +
  scale_x_date(date_breaks = "3 years", date_labels = "%Y") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(x = "Time", y = "Unit Nonresponse rate") +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Time.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Month
```{r}
monthly_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(month)) %>% 
  group_by(month) %>%
  summarise(unit_nonres_rate = mean(unit_nonres == 1), .groups = 'drop')

p_des <- ggplot(monthly_rate, aes(x = month, y = unit_nonres_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +  
  labs(x = "Month", y = "Unit nonresponse rate") +
  theme_minimal()

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Month.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Region
```{r}
region_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(vg_westeast)) %>%
  group_by(vg_westeast) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = 'drop')

p_des <- ggplot(region_rate, aes(x = vg_westeast, y = unit_nonres_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +  
  labs(x = "Region", y = "Unit nonresponse rate") +
  theme_minimal()

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Region.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Sector
```{r}
sector_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(sector_total)) %>%
  group_by(sector_total) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = "drop")

p_des <- ggplot(sector_rate, aes(x = reorder(sector_total, unit_nonres_rate),
                             y = unit_nonres_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Sector", y = "Unit nonresponse rate") +
  coord_flip() +
  theme_minimal(base_size = 12)

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Sector.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Particip number (optional)
```{r}
particip_rate <- unit_nonresponse_data_des %>%
  group_by(particip_num) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = "drop") %>%
  filter(!is.na(particip_num))
  
p_des <- ggplot(particip_rate, aes(x = particip_num, y = unit_nonres_rate)) +
  geom_line()+
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(x = "Participation Number", y = "Unit Nonresponse rate") +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Particip.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Particip number + Variability Bands
```{r}
particip_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(particip_num)) %>%
  group_by(particip_num) %>%
  summarise(
    n = n(),
    unit_nonres_rate = mean(unit_nonres),
    se = sqrt(unit_nonres_rate * (1 - unit_nonres_rate) / n),
    lower = unit_nonres_rate - 1.96 * se,
    upper = unit_nonres_rate + 1.96 * se,
    .groups = "drop"
  )

p_des <- ggplot(particip_rate,
                aes(x = particip_num, y = unit_nonres_rate)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25) +
  geom_line() +
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(
    x = "Participation Number",
    y = "Unit nonresponse rate"
  ) +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Particip_vb.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Particip number Count
```{r}
particip_count <- unit_nonresponse_data_des %>%
  count(particip_num)

p_des <- ggplot(particip_count, aes(x = particip_num, y = n)) +
  geom_line() +
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  labs(
    x = "Participation Number",
    y = "Number of observations"
  ) +
  theme_minimal()

p_des

ggsave("outputs/Particip_count.pdf", p_des, device = "pdf", width = 8, height = 4.5)
write.csv(particip_count, file = 'outputs/particip_count.csv', row.names = FALSE)
```

# Unit Nonresonse Rate by Particip length (optional)
```{r}
particip_length_rate <- unit_nonresponse_data_des %>%
  group_by(particip_length) %>%
  summarise(unit_nonres_rate = mean(unit_nonres))
  

p_des <- ggplot(particip_length_rate, aes(x = particip_length, y = unit_nonres_rate)) +
  geom_line()+
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(x = "Participation Length", y = "Unit nonresponse rate") +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_particip_length.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Particip length + Variability Bands
```{r}
particip_length_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(particip_length)) %>%
  group_by(particip_length) %>%
  summarise(
    n = n(),
    unit_nonres_rate = mean(unit_nonres),
    se = sqrt(unit_nonres_rate * (1 - unit_nonres_rate) / n),
    lower = unit_nonres_rate - 1.96 * se,
    upper = unit_nonres_rate + 1.96 * se,
    .groups = "drop"
  )

p_des <- ggplot(particip_length_rate,
                aes(x = particip_length, y = unit_nonres_rate)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.25) +
  geom_line() +
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(
    x = "Participation Length",
    y = "Unit nonresponse rate"
  ) +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_particip_length_vb.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Particip Length Count
```{r}
particip_length_count <- unit_nonresponse_data_des %>%
  count(particip_length)

p_des <- ggplot(particip_length_count, aes(x = particip_length, y = n)) +
  geom_line() +
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  labs(
    x = "Participation Length",
    y = "Number of observations"
  ) +
  theme_minimal()

p_des

ggsave("outputs/Particip_length_count.pdf", p_des, device = "pdf", width = 8, height = 4.5)
write.csv(particip_length_count, file = 'outputs/particip_length_count.csv', row.names = FALSE)
```

# local cor(number, length)

```{r}
k <- 15

local_corr <- map_dfr(1:400, function(L) {
  
  sub <- unit_nonresponse_data_des %>%
    filter(
      particip_length >= L - k,
      particip_length <= L + k
    )
  
  if (nrow(sub) < 30) return(NULL)  
  
  tibble(
    length_center = L,
    pearson_cor = cor(sub$particip_length, sub$particip_num),
    spearman_cor = cor(sub$particip_length, sub$particip_num, method = "spearman"),
    n_obs = nrow(sub)
  )
})


p_des <- ggplot(local_corr, aes(x = length_center, y = pearson_cor)) +
  geom_line(alpha = 0.8) +
  geom_smooth(se = FALSE, method = "loess", color = "black") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_x_continuous(limits = c(1, NA), 
                     breaks = function(x) {
                       unique(c(1, scales::pretty_breaks()(x)))},
                     expand = expansion(mult = c(0, 0.02))) +
  labs(
    x = "Participation Length",
    y = "Local correlation between Length and Number"
  ) +
  theme_minimal(base_size = 12)

p_des

ggsave("outputs/Local_correlation_particip.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by avg BS (UNROUNDED)
```{r}
avg_BS_unround_rate <- unit_nonresponse_data_des %>%
  group_by(vg_statebus_past6m) %>%
  summarise(unit_nonres_rate = mean(unit_nonres)) %>%
  filter(!is.na(vg_statebus_past6m))
  

p_des <- ggplot(avg_BS_unround_rate, aes(x = vg_statebus_past6m, y = unit_nonres_rate)) +
  geom_line()+
  geom_point(size = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(x = "Average BS over Past Six Months", y = "Unit Nonresponse rate") +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_AVG_BS.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# avg BS count
```{r}
avg_bs_count <- unit_nonresponse_data_des %>%
  count(vg_statebus_past6m)

p_des <- ggplot(avg_bs_count, aes(x = vg_statebus_past6m, y = n)) +
  geom_col() +
  scale_y_continuous(
    breaks = scales::pretty_breaks(n = 20),
    labels = scales::comma) +
  labs(
    x = "Average BS over Past Six Months",
    y = "Number of observations"
  ) +
  theme_minimal()

p_des

ggsave("outputs/avg_bs_count.pdf", p_des, device = "pdf", width = 8, height = 4.5)
write.csv(avg_bs_count, file = 'outputs/avg_bs_count.csv', row.names = FALSE)
```

# Unit Nonresonse Rate by avg BE (UNROUNDED)
```{r}
avg_BE_unround_rate <- unit_nonresponse_data_des %>%
  group_by(vg_comexp_past6m) %>%
  summarise(unit_nonres_rate = mean(unit_nonres)) %>%
  filter(!is.na(vg_comexp_past6m))
  

p_des <- ggplot(avg_BE_unround_rate, aes(x = vg_comexp_past6m, y = unit_nonres_rate)) +
  geom_line()+
  geom_point(size = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  labs(x = "Average BE over Past Six Months", y = "Unit Nonresponse rate") +
  theme_minimal() +
  theme(plot.title = element_blank())

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_AVG_BE.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# avg BE count
```{r}
avg_be_count <- unit_nonresponse_data_des %>%
  count(vg_comexp_past6m)

p_des <- ggplot(avg_be_count, aes(x = vg_comexp_past6m, y = n)) +
  geom_col() +
  scale_y_continuous(
    breaks = scales::pretty_breaks(n = 20),
    labels = scales::comma) +
  labs(
    x = "Average BE over Past Six Months",
    y = "Number of observations"
  ) +
  theme_minimal()

p_des

ggsave("outputs/avg_be_count.pdf", p_des, device = "pdf", width = 8, height = 4.5)
write.csv(avg_be_count, file = 'outputs/avg_be_count.csv', row.names = FALSE)
```

# Unit Nonresonse Rate by Size
```{r}
size_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(vg_size)) %>% 
  group_by(vg_size) %>%
  summarise(missing_rate = mean(unit_nonres == 1), .groups = 'drop')  

p_des <- ggplot(size_rate, aes(x = vg_size, y = missing_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +  
  labs(x = "Company Size", y = "Unit nonresponse rate") +
  theme_minimal()

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Company_Size.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by Online Status
```{r}
online_rate <- unit_nonresponse_data_des %>%
  group_by(online) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = 'drop')

p_des <- ggplot(online_rate, aes(x = online, y = unit_nonres_rate)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = percent(unit_nonres_rate, accuracy = 0.001)),
            vjust = -0.5, size = 3) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +  
  labs(x = "Online Status", y = "Unit nonresponse rate") +
  theme_minimal()

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_Online.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```

# Unit Nonresonse Rate by festatifo
```{r}
fedstaifo_rate <- unit_nonresponse_data_des %>%
  filter(!is.na(fedstaifo)) %>%
  group_by(fedstaifo) %>%
  summarise(unit_nonres_rate = mean(unit_nonres), .groups = 'drop')
  #filter(!fedstaifo=='')

p_des <- ggplot(fedstaifo_rate, aes(x = reorder(fedstaifo, unit_nonres_rate),
                             y = unit_nonres_rate)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "State", y = "Unit nonresponse rate") +
  coord_flip() +
  theme_minimal(base_size = 12)

p_des

ggsave("outputs/Unit_Nonresponse_Rate_by_State.pdf", p_des, device = "pdf", width = 8, height = 4.5)
```
